Binary companions of red giant stars in \apogee\ \DR

### 2018-03-08 paper/1-catalog/twoface-catalog.tex
update figure titles
Big figures to end and table caption

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\nhighK}{4,510}
\newcommand{\nmultimodal}{XX}
\newcommand{\nunimodal}{319}

@@

\begin{table}
    \centering
    \begin{tabular}{c | c}
    \texttt{APOGEE\_ID} & \texttt{lnK\_per\_1} \\
    \hline
    2M00000002+7417074 & -2.028 \\
    2M00000068+5710233 & -2.600 \\
    2M00000222+5625359 &  2.134 \\
    2M00000446+5854329 & -7.199 \\
    2M00000535+1504343 & -4.457 \\
    2M00000546+6152107 & -4.388 \\
    2M00000797+6436119 & -0.774 \\
    2M00000866+7122144 & -3.313 \\
    ... & ...
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

@@

\subsection{Confident companions with effectively uniquely determined orbits}
\label{sec:catalog-unimodal}

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when
\begin{equation}
    P_{\textrm{max}} - P_{\textrm{min}} < \Delta \label{eq:unimodal}
\end{equation}
(see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior pdfs for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} (MAP) sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
We additionally join with the \apogee\ \DR\ \texttt{allStar} catalog and provide
all columns from this catalog for convenience.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all
columns in the high-$K$, unimodal sample catalog, available online.
\todo{where?}

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters; These stars are prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:unimodal}): If the samples in each respective cluster
are unimodal, we call the sampling ``bimodal.''

\figurename~\ref{fig:highK-bimodal} shows a few examples of stars that meet
this criterion.
In many of these cases, there are certain times at which a future observation
would be far more informative.
Visually, those times correspond to regions of time when the predicted RVs have
large variance based on the posterior samples at hand.
% For example, \todo{top panel, time X vs. time Y, node vs. large variance}.

\tablename~\ref{fig:highK-bimodal} contains ...
\todo{Describe catalog contents: Also include M2min and primary mass when
possible?}

\begin{table}
    \centering
    \begin{tabular}{c | c | c | c}
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 \\
    ... & ... & ...
    \end{tabular}
    \caption{\todo{copy pasta}This table contains \texttt{APOGEE\_ID}'s for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{schwimmbad} (\todo{JOSS paper}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}),
    \package{thejoker} (\todo{thejoker zenodo?}),
    \package{twobody} (\todo{twobody zenodo?}).
}

@@

>>>>

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\nhighK}{4,510}
\newcommand{\nbimodal}{113}
\newcommand{\nunimodal}{319}

@@

\begin{table}
    \centering
    \begin{tabular}{c | c}
    \texttt{APOGEE\_ID} & \texttt{lnK\_per\_1} \\
    \hline
    2M00000002+7417074 & -2.028 \\
    2M00000068+5710233 & -2.600 \\
    2M00000222+5625359 &  2.134 \\
    2M00000446+5854329 & -7.199 \\
    ... & ...
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

@@

\subsection{Confident companions with uniquely-determined orbits}
\label{sec:catalog-unimodal}

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when
\begin{equation}
    P_{\textrm{max}} - P_{\textrm{min}} < \Delta \label{eq:unimodal}
\end{equation}
(see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior pdfs for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} (MAP) sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
We additionally join with the \apogee\ \DR\ \texttt{allStar} catalog and provide
all columns from this catalog for convenience.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all
columns in the high-$K$, unimodal sample catalog, available online.
\todo{Link to a webpage with the catalogs and info on how to use with
TwoBody/TheJoker}

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters; These stars are prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples in period.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
We initialize the cluster positions at either end of the range of possible
periods.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:unimodal}).
If the samples in each respective cluster are unimodal, we call the sampling
``bimodal''; \nbimodal\ systems are identified as bimodal.

\figurename~\ref{fig:highK-bimodal} shows a few examples of systems that meet
this criterion.
In many of these cases, there are certain times at which a future observation
would be far more informative.
Visually, those times correspond to regions of time when the predicted RVs have
large variance based on the posterior samples at hand.
For example, in the bottom left panel of \figurename~\ref{fig:highK-bimodal}, an
observation at $t = 60$ would rule out one of the two possible orbits.

\tablename~\ref{tbl:highK-bimodal} contains a list of all \apogee\ targets with
bimodal samplings identified in this way.
The table contains two rows for each source, with the period, eccentricity, and
velocity semi-amplitude values from the MAP sample from each period mode.

\begin{table}
    \centering
    \begin{tabular}{c | c | c | c}
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 \\
    ... & ... & ...
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s and limited orbital
    parameter information for all \nbimodal\ stars identified as having bimodal
    posterior samplings in orbital period.
    Each source is listed twice, with MAP values of period, \texttt{P},
    eccentricity, \texttt{e}, and velocity semi-amplitude, \texttt{K}, from each
    period mode of the posterior sampling for the source.
    }
    \label{tbl:highK-bimodal}
\end{table}

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scikit-learn} (\citealt{Pedregosa:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{schwimmbad} (\todo{JOSS paper}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}),
    \package{thejoker} (\todo{thejoker zenodo?}),
    \package{twobody} (\todo{twobody zenodo?}).
}

@@

\section{Example data and orbit samples}
